SPIRAL OPTIMIZATION ALGORITHM

### 2021-10-17 Semester I/Analisis Numerik Lanjut/Tugas Kerang/spiral.Rmd
fix

# untuk sistem persamaan
ikanx_2 = function(f,a,b){
  x = seq(a,b,by = .25)

  temp_plot =
    expand.grid(x,x) %>%
    rename(x = Var1,
           y = Var2) %>%
    mutate(z = f(x,y)) %>%
    filter(round(z,3) == 0)

>>>>

# untuk sistem persamaan
ikanx_2 = function(f,a,b){
  x = seq(a,b,by = .1)

  temp_plot =
    expand.grid(x,x) %>%
    rename(x = Var1,
           y = Var2) %>%
    mutate(z = f(x,y)) %>%
    filter(round(z,1) == 0)
